Quality Definitions of Qualities

### 2019-12-03 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
Done with Reliability and Correctness

\begin{defn}
	Installability is related to the amount of human effort required to install a
	software in a designated environment \citep{iso2001iec}
		{ berander2005software}.
\end{defn}

\begin{defn}
	The capability of a software product to be installed in a specified
	environment \citep{berander2005software}.  \wss{remove the quotation marks -
		we are assuming all definitions are directly quoted from the source.  Please
		remove quotes for all of the definitions that you ``own.''} 
\end{defn}

\begin{defn} \label{InstallabilityDefnSelected1}
	``The efficacy of the installation, uninstallation or reinstallation process
	of a software product in a specified environment'' \citep{iso201017043}
\end{defn}

\begin{defn}
	The degree of effectiveness and efficiency with which a product or system can
	be successfully installed and/or uninstalled in a specified environment
	\citep{ISO/IEC25010}.
\end{defn}

\begin{defn} \label{InstallabilityDefnSelected2}
	Installability refers to the cost or effort required for the installation of a
	software or product, given an installation is possible to begin with
	\citep{lenhard2013measuring}
\end{defn}

@@

\wss{The rationale is missing.  Please add.}
\oo{The definition allows to measure the cost both from system and human view
	points}

\subsection{\notdone{Correctness} \oo{owner}}

\begin{defn}
	The degree to which a software's specification is satisfied
	\citep{berander2005software}.
\end{defn}

\begin{defn} \label{CorrectDefnSelected} 
	A software is correct if it functions according to its specified functional
	and non-functional specification \citep{GhezziEtAl2003}.  \wss{This is not how
		\citet{GhezziEtAl2003} defines correctness.  They only require satisfaction
		of the functional requirements.}

@@

\begin{defn}
	According to \citet{wilson2009quality}, ``the degree to which a system is free
	from defects in its specification, design, and implementation, is its
	correctness.''
\end{defn}

\begin{defn}
	``The ability of software products to perform their exact tasks, as defined by
	their specification'' \citep{meyer1988object}.
\end{defn}

\begin{defn}
	``The extent to which a program satisfies its specifications and fulfills the
	user's mission objectives'' \citep{McCallEtAl1977}. (As summarized in
	\citet{VanVliet2000}.)
\end{defn}

\begin{defn}
	``A program is functionally correct if it behaves according to its stated
	functional specifications'' \citep{ghezzi1991fundamentals}.
\end{defn}

@@

Definition~\ref{CorrectDefnSelected}

There is no direct tool or method for measuring correctness. One way of building
confidence in correctness is by reviewing to ensure that each requirement stated
is one that the stakeholders and experts desire.  By maintaining traceability,
consistency and unambiguity, we can reduce the occurrence of errors and make the
goal of reviewing for correctness easier.

The quality of a software's operation is dependent on the degree of correctness
\citep{berander2005software}. Correctness and reliability are said to have
dependencies, such that if a system exhibits a high degree of correctness then
it tends to be reliable \citep{GhezziEtAl2003}.

\subsection{\notdone{Verifiability} \oo{owner}}

@@

\begin{defn}
	A set of attributes that relate to the capability of software to maintain its
	level of performance under stated conditions for a stated period of time \citep{international2001iso}. (As summarized in \citep{berander2005software}.)
\end{defn}

\begin{defn} \label{reliabilitySelected1}
	Probability of failure-free operation of a computer program in a specified environment for a specified time \citep{musa1987software}. (As stated in \citep{pressman2005software}.)
\end{defn}

@@

>>>>

\begin{defn}
	The capability of a software product to be installed in a specified
	environment \citep{iso2001iec}. (As summarized in \citep{berander2005software}.)  \wss{remove the quotation marks -
	we are assuming all definitions are directly quoted from the source. Please
	remove quotes for all of the definitions that you ``own.''}
    \oo{Done} 
\end{defn}

\begin{defn} \label{InstallabilityDefnSelected2}
	The degree of effectiveness and efficiency with which a product or system can
	be successfully installed and/or uninstalled in a specified environment
	\citep{ISO/IEC25010}.
\end{defn}

\begin{defn} \label{InstallabilityDefnSelected1}
	Installability refers to the cost or effort required for the installation, given an installation is possible to begin with
	\citep{lenhard2013measuring}.
\end{defn}

@@

\wss{The rationale is missing.  Please add.}
The definition captures the cost or effort - human or machine, and considers not just the initial installation but uninstallation and re-installation which are all related to installation activities.
\oo{Done installability}
\subsection{\notdone{Correctness} \oo{owner}}

\begin{defn}  
	A program is functionally correct if it behaves according to its stated
   functional specifications \citep{GhezziEtAl2003}.  \wss{This is not how
		\citet{GhezziEtAl2003} defines correctness.  They only require satisfaction
		of the functional requirements.} \oo{Updated}

@@

\begin{defn}
	According to \citet{wilson2009quality}, the degree to which a system is free
	from defects in its specification, design, and implementation, is its
	correctness.
\end{defn}

\begin{defn}
	The ability of software products to perform their exact tasks, as defined by
	their specification \citep{meyer1988object}.
\end{defn}

\begin{defn} \label{CorrectnessSelected}
	The extent to which a program satisfies its specifications and fulfills the
	user's mission objectives \citep{McCallEtAl1977}. (As summarized in
	\citet{VanVliet2000}.)
\end{defn}

\begin{defn}
 The term correctness is often mentioned as a degree to which software meets the requirement specification \citep{IEEEStdGlossarySET1990}.
\end{defn}

\begin{defn}
	Correctness from software engineering perspective can be defined as the adherence to the specifications that determine how users can interact with the software and how the software should behave when it is used correctly \citep{Tutorialspoint}.
\end{defn}

@@

Definition~\ref{CorrectnessSelected} rephrased: The extent to which a software product satisfies its functional and non-functional specifications and fulfills the
user's mission objectives.

\noindent \textbf{Reasoning}
To determine whether a program is correct, we must be able to refer to both its functional and non-functional requirements to understand the intended purpose and based on defined metrics, determine the extent to which this is met. Most definitions of correctness refers only to functional specifications but this is rephrased to include the non-functionals.
There is no direct tool or method for measuring correctness. One way of building
confidence in correctness is by reviewing to ensure that each requirement stated
is one that the stakeholders and experts desire.  By maintaining traceability,
consistency and unambiguity, we can reduce the occurrence of errors and make the
goal of reviewing for correctness easier.

The quality of a software's operation is dependent on the degree of correctness
\citep{berander2005software}. Correctness and reliability are said to have
dependencies, such that if a system exhibits a high degree of correctness then
it tends to be reliable \citep{GhezziEtAl2003}. \oo{Done Correctness}
\subsection{\notdone{Verifiability} \oo{owner}}

@@

\begin{defn}
	A set of attributes that relate to the capability of software to maintain its
	level of performance under stated conditions for a stated period of time \citep{iso2001iec}. (As summarized in \citet{berander2005software}.)
\end{defn}

\begin{defn} \label{reliabilitySelected1}
	Probability of failure-free operation of a computer program in a specified environment for a specified time \citep{musa1987software}. (As stated in \citet{pressman2005software}.)
\end{defn}

@@

\begin{defn}
	Informally, the reliability of a system is the probability, over a given
	period of time, that the system will correctly deliver services as expected by
	the user \citep{sommerville}
\end{defn}
